Measurement and Probability in Fuzzy Quantum Theories

### 2017-01-25 prop.tex
prop.tex \section{Increasing the Measurement Resource} Updating...

If $\bar{f}$ has a non-empty core, $\bar{f}$ must be in the above
case 1 - 3 so that $\bar{f}^{-1}\left(\imposs\right)\cap S^{2}$ contains
no area in $S^{2}$.\footnote{Notice that we only discuss the part of $\bar{f}^{-1}\left(\imposs\right)$
which is in $S^{2}$. In general, we could discuss the whole $\bar{f}^{-1}\left(\imposs\right)\subseteq\mathbb{C}S^{2}$.
However, restricting to $S^{2}$ enable us to visualize and imagine
easily. Also, if a interval-valued frame function~$\bar{f}$ has
an empty core when restricting to $S^{2}$, $\bar{\mu}$ has an empty
core on the original space as well. So restricting to $S^{2}$ still
provides valid results.} In contrast, if $\bar{f}^{-1}\left(\imposs\right)\cap S^{2}$ contains
some area in $S^{2}$, it must be the situation of case 4, and $\bar{f}$
has an empty core. Furthermore, the larger the area, the more state
vectors which are inconsistent with any particular Born rule frame
function. Therefore, the area of $\bar{f}^{-1}\left(\imposs\right)\cap S^{2}$
could indicate how much $\bar{f}$ deviate from the Born rule frame
functions.

@@

\begin{definition}Given a vector~$\ket{\psi}\in S^{2}$ with a specified
north pole~$\ket{0}\in S^{2}$, then $\theta\left(\ket{\psi}\right)=\arccos\ip{0}{\psi}$
denotes the the latitude of $\ket{\psi}$.\end{definition}

>>>>

If $\bar{f}$ has a non-empty core, $\bar{f}$ must be in the above
case 1 - 3 so that $\bar{f}^{-1}\left(\imposs\right)\cap S^{2}$ contains
no area in $S^{2}$.\footnote{Notice that we only discuss the part of $\bar{f}^{-1}\left(\imposs\right)$
in $S^{2}$. In general, we could discuss the whole $\bar{f}^{-1}\left(\imposs\right)\subseteq\mathbb{C}S^{2}$.
However, restricting to $S^{2}$ enable us to visualize and imagine
easily. Also, if a interval-valued frame function~$\bar{f}$ has
an empty core when restricting to $S^{2}$, $\bar{f}$ has an empty
core on the original space as well. So restricting to $S^{2}$ still
provides some valid results.} In contrast, if $\bar{f}^{-1}\left(\imposs\right)\cap S^{2}$ contains
some area in $S^{2}$, it must be the situation of case 4, and $\bar{f}$
has an empty core. Furthermore, the larger the area, the more state
vectors which are inconsistent with any particular Born rule frame
function. Therefore, the area of $\bar{f}^{-1}\left(\imposs\right)\cap S^{2}$
could indicate how much $\bar{f}$ deviate from the Born rule frame
functions. In the following paragraphs, we will establish that if
the area of $\bar{f}^{-1}\left(\imposs\right)\cap S^{2}$ is big,
then the interval~$\mathscr{I}$ must be coarse. Therefore, if the
interval~$\mathscr{I}$ is finer, then the area of $\bar{f}^{-1}\left(\imposs\right)\cap S^{2}$
would be smaller so that $\bar{f}$ is closer to a Born rule frame
function.

@@

\begin{definition}Given a vector~$\ket{\psi}\in S^{2}$ with a specified
north pole~$\ket{0}\in S^{2}$, then $\theta\left(\ket{\psi}\right)=\arccos\ip{0}{\psi}$
denotes the latitude of $\ket{\psi}$. Conversely, $\theta^{-1}\left(I\right)=\set{\ket{\psi}\in S^{2}}{\theta\left(\ket{\psi}\right)\in I}$.
For example, $\theta^{-1}\left(\left[\theta_{0},\frac{\pi}{2}\right]\right)=\set{\ket{\psi}\in S^{2}}{\theta_{0}\le\theta\left(\ket{\psi}\right)\le\frac{\pi}{2}}$
contains all states whose latitude is larger than $\theta_{0}$.\end{definition}

\begin{lemma}Given $\theta_{0}\in\left[0,\frac{\pi}{2}\right]$,
if $\bar{f}\left(\ket{\psi}\right)=\imposs$ for every $\ket{\psi}\in\theta^{-1}\left(\left[\theta_{0},\frac{\pi}{2}\right]\right)$,
then for any $\ket{\psi_{0}}$ and $\ket{\psi_{1}}\in\theta^{-1}\left(\left[0,\theta_{0}\right]\right)$,
$\bar{f}\left(\ket{\psi_{0}}\right)=\bar{f}\left(\ket{\psi_{1}}\right)$.\end{lemma}
